A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-05-17 related.tex
todo resolved
reviewer1 - revision#6 - more related work

@@

\cite{alon2019code2vec} presented code2vec, a neural model for representing code snippets as fixed size vectors. In their approach, they extracted flattened paths from the AST, and stored all the leaf-to-leaf paths. The intuition behind this decision was that leaf-to-leaf paths tend to encode more semantic information than root-to-leaf paths. They associated a fixed size vector with each path, and fed these as inputs to a neural network that learns how to aggregate all these paths to a single embedding. Our code embedding approach is simpler than code2vec's, as we have a specific (and simpler) goal---we aim to cluster bug patterns, not predict method names. Moreover, unlike us, code2vec does not offer a general code embedding method, since the final embedding depends on the output layer of the neural network. That is, if we change the goal of method name prediction, the embeddings would be completely different. Also, unlike many embeddings, our code embedding is interpretable: our columns are associated with non terminals. We have used the interpretability in our experiments. In code2vec, the layout of the final vector is a parameter of the system and  is not related to the underlying programming language.

Our work tends to be more similar to that of~\cite{hanam2016discovering}. However, our novel program embedding approach differs from what they did on certain key decisions. In~\cite{hanam2016discovering}, they introduced the Feature Properties table, which is a categorization for program elements. Embedding programs based on this table resulted in an order-sensitive embedding, however, it made the datapoints sparse. Our datapoints are more dense than theirs. \todo[inline]{quantify?}

>>>>

\subsection{Automated Patch Correctness Assessment}

Overfitting poses a substantial challenge for automated program repair (APR) systems, where synthesized patches may pass test cases but fail to be correct. Automated patch correctness assessment (APCA) aims to inspect the correctness of generated patches using dynamic and static analyses. While our project has a different objective than APCA, we share similarities in design decisions with APCA systems, particularly in feature extraction. \cite{ye2021automated} propose ODS, an overfitting patch detection system, which assumes that code features capturing universal correctness properties can be utilized to classify overfitting patches across program repair systems and software projects. ODS extracts 202 manually crafted code features by comparing fixed and buggy code and employs supervised learning to build a distributional model for classifying unseen patches, achieving over 70\% accuracy in evaluations on Defects4J, Bugs.jar, and Bears benchmarks. Similarly, our feature extraction involves manual crafting of features. In another study, \cite{tian2022change} present an enhanced APCA model that transforms the problem into a question-answering scenario and incorporates a neural architecture to learn semantic correlations between bug reports and commit messages. Additionally, \cite{lin2022context} introduce \textsc{Cache}, a neural-based context-aware AST embedding method that captures both the change part and the unchanged part (context code) of patches. Evaluation results demonstrate that context knowledge significantly enhances the performance and accuracy of APCA systems.

@@

\cite{alon2019code2vec} presented code2vec, a neural model for representing code snippets as fixed size vectors. In their approach, they extracted flattened paths from the AST, and stored all the leaf-to-leaf paths. The intuition behind this decision was that leaf-to-leaf paths tend to encode more semantic information than root-to-leaf paths. They associated a fixed size vector with each path, and fed these as inputs to a neural network that learns how to aggregate all these paths to a single embedding. Our code embedding approach is simpler than code2vec's, as we have a specific (and simpler) goal---we aim to cluster bug patterns, not predict method names. Moreover, unlike us, code2vec does not offer a general code embedding method, since the final embedding depends on the output layer of the neural network. That is, if we change the goal of method name prediction, the embeddings would be completely different. Also, unlike many embeddings, our code embedding is interpretable: our columns are associated with non terminals. We have used the interpretability in our experiments. In code2vec, the layout of the final vector is a parameter of the system and  is not related to the underlying programming language. Building on the same ideas, as a subsequent work, the same authors also introduced code2seq~\citep{alon2019code2seq}, an approach for transforming a code snippet to a sequence encoding. They evaluated their work on three seq2seq use cases: (1) method name prediction, (2) code captioning, and (3) code documentation. code2seq proved to have a better understanding of syntactical structure of the code and outperformed previous neural machine translation systems.

\cite{hoang2020cc2vec} introduced CC2Vec, a neural network model that utilizes log messages accompanying code changes to learn representations capturing the semantic information. By addressing challenges in distinguishing between added and removed code and incorporating an attention mechanism, CC2Vec outperforms previous techniques for code change representation. The model employs a hierarchical attention network, which incorporates a multi-level bidirectional GRU recurrent neural network, to encode information about changed code tokens, lines, and hunks into vectors representing added and removed changes. These vectors are then combined and fed into a hidden layer for predicting the target function. Evaluation across log message generation, bug fixing patch identification, and just-in-time defect prediction tasks demonstrates the superior performance of CC2Vec compared to state-of-the-art approaches in all three tasks.

Our work tends to be more similar to that of~\cite{hanam2016discovering}. However, our novel program embedding approach differs from what they did on certain key decisions. In~\cite{hanam2016discovering}, they introduced the Feature Properties table, which is a categorization for program elements. Embedding programs based on this table resulted in an order-sensitive embedding, however, it made the datapoints sparse. Our datapoints are more dense than theirs. More specifically, the number of our dimensions is more than 11x smaller.
